Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2014-12-08 manuscript.tex
Cite who used Tesseroids before
Revising accuracy section
Added some more sentences to explain the problem setup and reordered.

@@

The value chosen for this ratio determines how many divisions are made.

@@

@@

There has been no further investigation into
the relationship between values of the distance-size ratio and
the computation error.

It is also not clear whether the same value of $D$ used for the gravitational
attraction can be used for the gradient tensor components.

We need a reference value against which to compare the computed tesseroid effects.

The spherical shell is a convenient model with an analytical solution along
the polar axis.

@@

The largest errors in the GLQ integration occur directly on top of the
tesseroid but not exactly at it's center, as can be seen in
Figure~\ref{fig:glqerrorsample}.

@@

We calculate the effect of a tesseroid model of the spherical shell on a
regular grid.

@@

We repeated the tesseroid calculations with values of the distance-size ratio
varying from 0 (i.e., no divisions) to 10 in 0.5 intervals.

Figure~\ref{fig:tess_vs_shell} shows the maximum difference between the
shell and tesseroid fields as a function of the distance-size ratio.

Differences are given as a percentage of the shell value.

The curves allow us to choose a value of the distance-size ratio that
produces an acceptable error.

@@

All errors will be smaller than 0.1\% if one uses a distance-size ratio of 1.

Even in the extreme case of a $30^\circ$ tesseroid with computation points at a
height of 1 km above the tesseroid.

A distance-size ratio of 1.5 is sufficient to achieve errors below 0.1\% in
$g_z$.

A distance-size ratio of 8 is required to achieve errors below 0.1\% in
the gravity gradient components.

The error curve for the computation grid at 260 km height shows that
the error is smaller at higher altitudes.

Computation at higher altitudes would not change the chosen values of the
distance-size ratio for the potential and $g_z$.

@@

We computed the error curves for $g_{zz}$ only at different heights
(Figure~\ref{fig:gzz_error_height}).

>>>>

This article describes the software \textit{Tesseroids} and the implementation
of the adaptive discretization algorithm.

Previous versions of \textit{Tesseroids} have been used by, e.g.,
\citet{Alvarez2012, Bouman2013, Bouman2013a, Mariani2013, Braitenberg2014,
Braitenberg2011, Fullea2014}.

@@

@@

The value chosen for $D$ determines how many divisions are made.

@@

To our knowledge,
there has been no further investigation
into the relationship between
values of the distance-size ratio and the computation error.

It is also not clear whether
the same value of $D$ yields compatible error levels
for the gravitational attraction
and the gradient tensor components.

We must determine the relationship between the distance-size ratio $D$ and
the computation error.

We need a reference against which to compare the computed tesseroid fields.

The spherical shell is a convenient reference model.

The spherical shell has a analytical solutions for the gravitational potential,
attraction, and gradient tensor along the polar axis.

@@

We can use the spherical shell values to calculate the error of the tesseroid
computations for varying values of $D$.

@@

We calculate the effect of a tesseroid model on a regular grid.

@@

We calculate the difference between the shell values and the values computed
from tesseroids.

We keep only the largest difference.

Calculating on a grid above a tesseroid is important because
the largest errors in the GLQ integration occur directly on top of the
tesseroid but not exactly at it's center, as can be seen in
Figure~\ref{fig:glqerrorsample}.

The difference between shell and tesseroid values would be underestimated
if the computation was performed only at a single point on the polar axis.

We repeated the tesseroid calculations with values of the distance-size ratio
$D$ varying from 0 (i.e., no divisions) to 10 in 0.5 intervals.

Figure~\ref{fig:tess_vs_shell} shows the maximum difference between the
shell and tesseroid fields as a function of $D$.

The differences are given as a percentage of the shell value.

The error versus $D$ curves allow us to choose a value of $D$ that
results in an error below a chosen maximum.

@@

For $D=1$ all errors are smaller than 0.1\%,
even in the extreme case of a $30^\circ$ tesseroid with computation points at a
height of 1 km above the tesseroid.

$D=1.5$ is sufficient to achieve errors below 0.1\% in $g_z$.

$D=8$ is required to achieve errors below 0.1\% in
the gravity gradient components.

The error curves for the computation at 260 km height shows that
the error is smaller at higher altitudes for all fields.

Computation at 260 km height does not produce errors above the 0.1\% threshold
for the potential and $g_z$.

@@

We computed the error curves for $g_{zz}$ at different heights
(Figure~\ref{fig:gzz_error_height}).
